### 2019-10-29 paper/paper.tex
Insert the barreloid figure

>>>>

\cmnt{Start from the thalamic barreloids, to generate the interaction
  parameters}

% Include figure ../boundaries/barreloids_vanderloos_graph.png
\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{../boundaries/barreloids_vanderloos_graph.png}
\end{center}
\vspace{-2em}
\caption{Barreloid centres taken from \cite{van_der_loos_1976}, Fig.~2
  are shown as black circles. It is assumed that there are at least
  two linearly increasing, orthogonal signalling gradients in the
  thalamus (side graphs - addme!), such that the location of each
  barreloid within the graded thalamic signal field can differentiate
  the efferent axons, with the result that axons from each barreloid
  interact to varying degrees with cortical signalling
  gradients. Coloured arrows show, for each barreloid, the magnitude
  of the interaction that its thalamocortical projection will have
  with the four signalling gradients in the cortex. The mappings from
  barreloid location to interaction strength are linear.}
\label{fig:barreloids}
\end{figure*}
